---
title: "priors"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(brms)
library(extraDistr)
```

### Writing down what we know for the least informative prior

##### Intercept
Under sum contrast coding, this is the grand mean RT per word. Minimum RT is 0 ms. Maximum is unlikely to be greater than 3000


##### Fixed effects

It is quite unlikely that any between condition differences in RT are going to be greater than 600 ms. We will set the mean to be a small positive value, since we set up our contrasts so that the coefficients are expected to be positive. However, we will also assume that the effect can be positive or negative, and therefore specify 

##### Random effects

Lets assume that random slopes and random intercepts are not likely to be sampled from distributions with sds greater than 500



##### Residual variance

Lets assume that it is very unlikely our residual variance is going to be greater than 2000




### Prior 1

```{r}

prior1 <- c(prior("normal(300,1000)", class = "Intercept"),
                prior("normal(20,150)", class = "b"),  
                prior("normal(0,200)", class = "sd"),
                prior("normal(0,500)", class = "sigma"))

```


```{r}
## Intercept
hist(extraDistr::rtnorm(10000, mean = 300, sd = 1000, a = 0))
hist(rnorm(10000, mean = 300, sd = 1000))

```


```{r}

# fixed effects
hist(rnorm(100000, mean=20, sd = 150))

```


```{r}
# random effects
hist(rnorm(100000, mean=0, sd = 200))

```

```{r}

# residual variance
hist(rnorm(100000, mean=0, sd = 500))

```



```{r, cache=TRUE, include=FALSE}

verb_dat <- readRDS('./saved_objects/verb_dat')

prior1_fit_notrunc <- brm(corrected_rt ~ Type_num + (0 + Type_num | participant) + (1 + Type_num | item),
                      data=verb_dat,
                      cores = 4,
                      prior = prior1,
                      iter = 4000,
                      seed = 117,
                      sample_prior = "only")


prior1_fit<- brm(RT |trunc(lb=0) ~ Type_num + (0 + Type_num | participant) + (1 + Type_num | item),
                data=verb_dat,
                cores = 4,
                prior = prior1,
                iter = 4000,
                seed = 117,
                sample_prior = "only")


##note for corrected RT truncation won't work because there can be negative values!
```
**Non-truncated distribution**

```{r, cache=TRUE}

prior1_fit_samps_notrunc <-  data.frame(t(posterior_predict(prior1_fit_notrunc, ndraws=1000))) %>%
  gather(key='sim', value = 'pred_sample') 



ggplot(prior1_fit_samps_notrunc, aes(x = pred_sample)) + 
  geom_density()


## Plotting the difference between SRC and ORC 

post_samples <- posterior_samples(prior1_fit_notrunc) %>%
  select(starts_with('b_')) %>%
  gather(key=Parameter, val = 'Param_val', starts_with('b_'))
  

ggplot(post_samples, aes(y=Param_val, x = Parameter)) +
  geom_boxplot()  +
  facet_wrap(~Parameter, scales="free")



## Plotting the histograms for SRC and ORC

post_samples_bycond <-  posterior_samples(prior1_fit_notrunc) %>%
  mutate(RT_subj  = b_Intercept,
         RT_obj = b_Intercept + b_Type_num) %>%
  select(RT_subj, RT_obj) %>%
  gather(key = 'cond', value = 'RT', RT_subj, RT_obj) %>%
  group_by(cond) %>%
  summarise(mean = mean(RT),
            lower = quantile(RT, 0.025)[[1]],
            upper = quantile(RT, 0.975)[[1]]) 


ggplot(post_samples_bycond, aes(x = cond, y=mean)) + 
  geom_point(stat="identity", postion= position_dodge() ) + 
  geom_errorbar(aes(ymin=lower,
                    ymax=upper), 
                width=0.2) 



```



**Truncated distribution**
```{r, cache=TRUE}

prior1_fit_samps <-  data.frame(t(posterior_predict(prior1_fit, ndraws=1000))) %>%
  gather(key='sim', value = 'pred_sample') 



ggplot(prior1_fit_samps, aes(x = pred_sample)) + 
  geom_density()


## Plotting the difference between SRC and ORC 

post_samples <- posterior_samples(prior1_fit) %>%
  select(starts_with('b_')) %>%
  gather(key=Parameter, val = 'Param_val', starts_with('b_'))
  

ggplot(post_samples, aes(y=Param_val, x = Parameter)) +
  geom_boxplot()  +
  facet_wrap(~Parameter, scales="free")



## Plotting the histograms for SRC and ORC

post_samples_bycond <-  posterior_samples(prior1_fit) %>%
  mutate(RT_subj  = b_Intercept,
         RT_obj = b_Intercept + b_Type_num) %>%
  select(RT_subj, RT_obj) %>%
  gather(key = 'cond', value = 'RT', RT_subj, RT_obj) %>%
  group_by(cond) %>%
  summarise(mean = mean(RT),
            lower = quantile(RT, 0.025)[[1]],
            upper = quantile(RT, 0.975)[[1]]) 


ggplot(post_samples_bycond, aes(x = cond, y=mean)) + 
  geom_point(stat="identity", postion= position_dodge() ) + 
  geom_errorbar(aes(ymin=lower,
                    ymax=upper), 
                width=0.2) 



```


#### Prior 2

```{r, cache=TRUE}

prior2 <- c(prior("normal(300,1000)", class = "Intercept"),
                prior("normal(20,100)", class = "b"),  
                prior("normal(0,200)", class = "sd"),
                prior("normal(0,500)", class = "sigma"))

```


```{r}

# fixed effects
hist(rnorm(100000, mean=20, sd = 100))

```



```{r, cache=TRUE, include=FALSE}

prior2_fit <- brm(RT |trunc(lb=0) ~ Type_num + (0 + Type_num | participant) + (1 + Type_num | item),
                      data=verb_dat,
                      cores = 4,
                      prior = prior2,
                      iter = 4000,
                      seed = 117,
                      sample_prior = "only")

```

```{r, cache=TRUE}

prior2_fit_samps <-  data.frame(t(posterior_predict(prior2_fit, ndraws=1000))) %>%
  gather(key='sim', value = 'pred_sample') 



ggplot(prior2_fit_samps, aes(x = pred_sample)) + 
  geom_density()


## Plotting the difference between SRC and ORC 

post_samples <- posterior_samples(prior2_fit) %>%
  select(starts_with('b_')) %>%
  gather(key=Parameter, val = 'Param_val', starts_with('b_'))
  

ggplot(post_samples, aes(y=Param_val, x = Parameter)) +
  geom_boxplot()  +
  facet_wrap(~Parameter, scales="free")



## Plotting the histograms for SRC and ORC

post_samples_bycond <-  posterior_samples(prior2_fit) %>%
  mutate(RT_subj  = b_Intercept,
         RT_obj = b_Intercept + b_Type_num) %>%
  select(RT_subj, RT_obj) %>%
  gather(key = 'cond', value = 'RT', RT_subj, RT_obj) %>%
  group_by(cond) %>%
  summarise(mean = mean(RT),
            lower = quantile(RT, 0.025)[[1]],
            upper = quantile(RT, 0.975)[[1]]) 


ggplot(post_samples_bycond, aes(x = cond, y=mean)) + 
  geom_point(stat="identity", postion= position_dodge() ) + 
  geom_errorbar(aes(ymin=lower,
                    ymax=upper), 
                width=0.2) 




```

#### Prior 3


```{r, cache=TRUE}

prior3 <- c(prior("normal(300,1000)", class = "Intercept"),
                prior("normal(20,100)", class = "b"),  
                prior("normal(0,150)", class = "sd"),
                prior("normal(0,300)", class = "sigma"))

```

```{r}

# random effects
hist(rnorm(100000, mean=0, sd = 150))

```


```{r, cache=TRUE, include=FALSE}

prior3_fit <- brm(RT | trunc(lb=0) ~ Type_num + (0 + Type_num | participant) + (1 + Type_num | item),
                      data=verb_dat,
                      cores = 4,
                      prior = prior3,
                      iter = 4000,
                      seed = 117,
                      sample_prior = "only")

```

```{r, cache=TRUE}

prior3_fit_samps <-  data.frame(t(posterior_predict(prior3_fit, ndraws=1000))) %>%
  gather(key='sim', value = 'pred_sample') 



ggplot(prior3_fit_samps, aes(x = pred_sample)) + 
  geom_density()


## Plotting the difference between SRC and ORC 

post_samples <- posterior_samples(prior3_fit) %>%
  select(starts_with('b_')) %>%
  gather(key=Parameter, val = 'Param_val', starts_with('b_'))
  

ggplot(post_samples, aes(y=Param_val, x = Parameter)) +
  geom_boxplot() +
  facet_wrap(~Parameter, scales="free")



## Plotting the histograms for SRC and ORC

post_samples_bycond <-  posterior_samples(prior3_fit) %>%
  mutate(RT_subj  = b_Intercept,
         RT_obj = b_Intercept + b_Type_num) %>%
  select(RT_subj, RT_obj) %>%
  gather(key = 'cond', value = 'RT', RT_subj, RT_obj) %>%
  group_by(cond) %>%
  summarise(mean = mean(RT),
            lower = quantile(RT, 0.025)[[1]],
            upper = quantile(RT, 0.975)[[1]])


ggplot(post_samples_bycond, aes(x = cond, y=mean)) + 
  geom_point(stat="identity", postion= position_dodge() ) + 
  geom_errorbar(aes(ymin=lower,
                    ymax=upper), 
                width=0.2) 




```



